Placeholder Title... Something About Delegating Quantum Computations

### 2019-11-14 longoutput.tex
Updates from Overleaf

\begin{algorithm}
	\caption{Amplification with simple input}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+m}}\bra{\rho_i^{\otimes n+m}}$
		\Procedure{Amplification}{$\phi$}
		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
		\If{number of accepted copies $\geq \frac{1}{2}-\varepsilon$}
			\State Output the last $m$ registers
		\Else
			\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{observation}
	\autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers
\end{observation}

\begin{theorem}
	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, conditioned on this acceptance, $\mathcal{F}$ has probability at least $1-\frac{p}{\delta}$ to accept each register of the output.
\end{theorem}
\begin{proof}
	Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.

>>>>

\begin{algorithm}
	\caption{Amplification with simple input}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+m}}\bra{\rho_i^{\otimes n+m}}$
		\Procedure{Amplification}{$\phi$}
		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
		\If{number of accepted copies $\geq (\frac{1}{2}-\frac{\varepsilon}{2})n$}
			\State Output the last $m$ registers
		\Else
			\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{observation}
	If the input is of the form $\ket{\phi^{\otimes n+m}}$, \autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers.
\end{observation}

\begin{theorem}
	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, its output when accepted has less than $\frac{p}{\delta}$ probability to be rejected by $\mathcal{F}$.
\end{theorem}
\begin{proof}
	Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.
